---
title: "Homework 5"
author: "Ainsel Levitskaia-Collins, HL2710"
date: "2025-11-05"
output: github_document
---

```{r include = FALSE}
library(tidyverse)
```


### Problem 1

Function:

- [X] fixed group size
- [X] randomly draws "birthdays" for each person
- [X] checks whether there are duplicate birthdays in the group
- [X] returns `TRUE` or `FALSE` based on the result

```{r}
#' repeat_birthdays
#'
#' @param group_size The size of the sample for which birthdays will be selected
#'
#' @returns A boolean value for whether or not there are any overlapping birthdays within the sample
repeat_birthdays = function(group_size) {
  birthday_df <- data.frame(birthdays = sample(1:365, size = group_size, replace = TRUE)) %>% 
    group_by(birthdays) %>% 
    count(birthdays) %>% 
    arrange(desc(n))
  
  overlap <- FALSE
  
  for (i in 1:ncol(birthday_df)) {
    if (pull(birthday_df, n)[[1]] > 1) {
      overlap = TRUE
    }
  }
  
  overlap
}
```


Analysis:

- [ ] run above function 10,000 times for each group size between 2 and 50
- [ ] for each group size, compute the probability that at least two people in the group will share a birthday by averaging across the 10,000 simulation runs
- [ ] make a plot showing the probability as a function of group size
- [ ] comment on results